Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-09 2016-Weak-FH-Bisim/WeakBisim.tex
nom des etats dans Fig 4; correction dernier listing.

Finaly, we list here, in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet:

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
INFO  SimpleProtImpl2 - 
{P|->p_send(m:sva_SV6:1:1)},
[(msg=m:sva_SV0:12:1)/\((s_recv(msg))=(s_recv(m:sva_SV0:12:1)))],   {s1_msg := msg, s1_c := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----_in(m:sva_SV6:1:1)_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:2 ------------------------------------------------------------
		<s0_a0_r0>-----p_a:sva_SV7:1:2----><s0_a0_r0>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:3 ------------------------------------------------------------
		<s0_a0_r0>-----q_a:sva_SV9:1:4----><s0_a0_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:4 ------------------------------------------------------------
		<s1_a0_r0>-----p_a:sva_SV7:1:2----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:5 ------------------------------------------------------------
		<s1_a0_r0>-----q_a:sva_SV9:1:4----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
{},   [(s1_msg=m:sva_SV1:114:2)/\(s1_c=c:sva_SV1:114:2)
  /\((s_send(s1_msg, s1_c))=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))
  /\(msg=m:sva_SV1:114:2)/\(c=c:sva_SV1:114:2)
  /\((m_recv(msg, c))=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))],
{s2_c := s1_c, a1_msg := msg, a1_c := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:7 ------------------------------------------------------------
		<s2_a1_r0>-----p_a:sva_SV7:1:2----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:8 ------------------------------------------------------------
		<s2_a1_r0>-----q_a:sva_SV9:1:4----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
{},   [(a1_msg=m:sva_SV2:114:3)/\(a1_c=c:sva_SV2:114:3)
  /\((m_send(a1_msg, a1_c))=(m_send(m:sva_SV2:114:3, c:sva_SV2:114:3)))
  /\(msg=m:sva_SV2:114:3)/\(c=c:sva_SV2:114:3)
  /\((r_recv(msg, c))=(r_recv(m:sva_SV2:114:3, c:sva_SV2:114:3)))],
{r1_msg := msg, r1_c := c}
	OT:9 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a0_r1>

INFO  SimpleProtImpl2 - 
		{},   [],   {}
	OT:10 ------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:11 ------------------------------------------------------------
		<s2_a0_r1>-----p_a:sva_SV7:1:2----><s2_a0_r1>

INFO  SimpleProtImpl2 - 
{Q|->q_recv(m:sva_SV8:1:3, c:sva_SV8:1:3)},
[(r1_msg=m:sva_SV5:18:6)/\(r1_c=c:sva_SV5:18:6)
  /\((r_send(r1_msg, r1_c))=(r_send(m:sva_SV5:18:6, c:sva_SV5:18:6)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a0_r1>-----_out(m:sva_SV8:1:3, c:sva_SV8:1:3)_----><s2_a0_r2>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:13 ------------------------------------------------------------
		<s2_a0_r1>-----q_a:sva_SV9:1:4----><s2_a0_r1>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:14 ------------------------------------------------------------
		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:15 ------------------------------------------------------------
		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [],   {s1_c := s2_c+1}
	OT:16 --------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:17 ------------------------------------------------------------
		<s2_a0_r2>-----p_a:sva_SV7:1:2----><s2_a0_r2>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:18 ------------------------------------------------------------
		<s2_a0_r2>-----q_a:sva_SV9:1:4----><s2_a0_r2>

INFO  SimpleProtImpl2 - 
		{},   [],   {}
	OT:19 ------------------------
		<s2_a0_r2>-----_tau_----><s0_a0_r0>

DEBUG SimpleProtImpl2 - 
Global State: <s0_a0_r0>
===================
pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_msg <-{msg, } s1_c <-{0, s2_c+1, }}> <a0 vars: {}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a0_r1>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r1 vars: { r1_c <-{c, } r1_msg <-{msg, }}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a2 vars: {}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a0_r2>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r2 vars: {}>

@@

%% In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
%% - a tau-loop on each state
%% - a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).

Many weak should be added, e.g. Tau loops on states <s2\_a1\_r0>, <s2\_a2\_r0>, 
<s2\_a0\_r0>, encoding the loop.

>>>>

Finaly, we list here in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet.
This view uses variable names very close to the internal representation in the tool, allowing for tracability of generated fresh variables. For example:
\begin{itemize}
\item m:SV6:1:1 refers to a variable named ``m'' in the synchronisation vector ``SV6''; the last 2 numbers allows to distinguish different clones.
\item the other variable names reflect our naming policy: state variables are prefixed by the name of the state, holes actions by the name of the hole.
\end{itemize}

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]

{P|->p_send(m:SV6:1:1)},
[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_c := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----_in(m:SV6:1:1)_----><s1_a0_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))], {}
	OT:2 ------------------------------------------------------------
		<s0_a0_r0>-----p_a:SV7:1:2----><s0_a0_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:3 ------------------------------------------------------------
		<s0_a0_r0>-----q_a:SV9:1:4----><s0_a0_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:4 ------------------------------------------------------------
		<s1_a0_r0>-----p_a:SV7:1:2----><s1_a0_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:5 ------------------------------------------------------------
		<s1_a0_r0>-----q_a:SV9:1:4----><s1_a0_r0>

{},   [(s1_msg=m:SV1:114:2)/\(s1_c=c:SV1:114:2)
  /\((s_send(s1_msg, s1_c))=(s_send(m:SV1:114:2, c:SV1:114:2)))
  /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
  /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
{s2_c := s1_c, a1_msg := msg, a1_c := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:7 ------------------------------------------------------------
		<s2_a1_r0>-----p_a:SV7:1:2----><s2_a1_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:8 ------------------------------------------------------------
		<s2_a1_r0>-----q_a:SV9:1:4----><s2_a1_r0>

{},   [(a1_msg=m:SV2:114:3)/\(a1_c=c:SV2:114:3)
  /\((m_send(a1_msg, a1_c))=(m_send(m:SV2:114:3, c:SV2:114:3)))
  /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
  /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
{r1_msg := msg, r1_c := c}
	OT:9 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a0_r1>

		{},   [],   {}
	OT:10 ------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:11 ------------------------------------------------------------
		<s2_a0_r1>-----p_a:SV7:1:2----><s2_a0_r1>

{Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
[(r1_msg=m:SV5:18:6)/\(r1_c=c:SV5:18:6)
  /\((r_send(r1_msg, r1_c))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a0_r1>-----_out(m:SV8:1:3, c:SV8:1:3)_----><s2_a0_r2>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:13 ------------------------------------------------------------
		<s2_a0_r1>-----q_a:SV9:1:4----><s2_a0_r1>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:14 ------------------------------------------------------------
		<s2_a2_r0>-----p_a:SV7:1:2----><s2_a2_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:15 ------------------------------------------------------------
		<s2_a2_r0>-----q_a:SV9:1:4----><s2_a2_r0>

		{},   [],   {s1_c := s2_c+1}
	OT:16 --------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:17 ------------------------------------------------------------
		<s2_a0_r2>-----p_a:SV7:1:2----><s2_a0_r2>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:18 ------------------------------------------------------------
		<s2_a0_r2>-----q_a:SV9:1:4----><s2_a0_r2>

		{},   [],   {}
	OT:19 ------------------------
		<s2_a0_r2>-----_tau_----><s0_a0_r0>

Assignements of state variables:

Global State: <s0_a0_r0>
===================
pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>

Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_msg <-{msg} s1_c <-{0, s2_c+1}}> <a0 vars: {}> <r0 vars: {}>

Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a1 vars: { a1_msg <-{msg} a1_c <-{c}}> <r0 vars: {}>

Global State: <s2_a0_r1>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r1 vars: { r1_c <-{c} r1_msg <-{msg}}>

Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a2 vars: {}> <r0 vars: {}>

Global State: <s2_a0_r2>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r2 vars: {}>

@@

%% In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
%% - a tau-loop on each state
%% - a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
%%
%%Many weak should be added, e.g. Tau loops on states <s2\_a1\_r0>, <s2\_a2\_r0>, 
%%<s2\_a0\_r0>, encoding the loop.
